\section{Future Work \& Conclusion}
\label{section:conclusion}

The goal of this report is to create an application to recognize sentences on iOS
and assist handwriting so that handwriting can be on par with keyboard input.
Although it is imperfect, the heuristic used for ROI detection successfully
detect a word out of a sentence, and can cut handwritten illustration out from the other
part of document without requiring large amount of computation. Since current ROI detection
algorithm does not parse all the trajectory and instead seaches for the subsequence included
in ROI from the end of the sequence iteratively for the sake of speed, it is sometimes the case
that strokes that should be included in ROI intuitively are not included.
Future tasks include improving this point.
It should also be noted that current implementation cannot separate handwriting from handwritten illustrations,
therefore text recognition process is always performed even if the user is drawing an illustration.
To prevent this, we need to put another process to check whether the output of ROI detection is
an illustation or text. Putting that process into the pipeline is also a future work.

On the other hand, text recognition had a trade-off between speed and accuracy.
Future tasks include improving the accuracy of text recognition without slowing it down.
Since this work does not elaborate on collecting datasets, or hyperparameters search,
the starting point of improving the accuracy can be either of them.

Another example of future work is to perform more accurate text recognition and ROI detection
using an online method.In auto-completion, prediction using information on surrounding words,
and refinement of the method of presenting complement candidates can also be one of future works.
